\documentclass[12pt]{scrbook}

\usepackage{geometry}
\geometry{
    a5paper
}

\begin{document}
\title{Dragon Rock}
\subtitle{A fantasy role playing game for the Commodore TED series of computers}
\author{7Turtles Software}

\maketitle

\chapter*{Introduction}
Thank you very much for purchasing \textit{Dragon Rock}. We hope that you have as much fun playing as we had creating it. In order to have the best possible experience, please read this manual carefully.

\section*{Requirements}
\textit{Dragon Rock} is a fantasy role plaiyng game designed for the Commodore \textit{TED} series of computers. In order to run \textit{Dragon Rock}, you will need the following:
\begin{itemize}
    \item A Commodore TED series computer (C16, C116 or plus/4) with \textbf{64K of RAM}. Please note that the game will not work on an unexpanded C16 or C116.
    \item A Commodore 1541 compatible disc drive (1541, 1571, 1551). The use of a 1551 drive is strongly recommended. 
    \item A monochrome or -- recommended -- colour TV or monitor.
\end{itemize}

\section*{Before you start}
Before starting your journey through Tianad, please do take the time and make a backup of the supplied game disc\footnote{Note that the disc is 2-sided; in order to make a complete backup, you have to copy side 1 \textit{and} side 2 of the game disc.} and use the game from your backup disc only, keeping the original in a safe location. 

\section*{If things go wrong}
A lot of time and effort went into the creation of \textit{Dragon Rock}. Nevertheless we can't be sure that the game is entirely bug-free. Should you happen to stumble upon an error in the game (or get stuck in any other way), please contact us at \texttt{dr@7turtles.de}


\chapter{The story so far\dots} 

For the longest time, everything seemed to be going just right in the Tianad province. The people were happy - perhaps amongst the happiest people in all of the great kingdom. 

And why wouldn't they? 

The summers were warm and winters mild, harvest had been great and plentiful for years on end now, commerce was flourishing, the roads were reasonably secure, almost every citizen of Tianad had enough to eat and drink and a roof over their heads... it really seemed as if the gods were smiling down on the little province on the southeast border of Nacordia. 

The change came slowly. At first, no one really noticed how fewer and fewer merchants from foreign lands were to be seen in the five major cities of Tianad. But then, as food and drink got scarce, stories of people disappearing from the roads at night were told in hushed voices in Tianads ever less frequented inns. 

Then the raids started. Troops of all kinds of monsters and thieves started paying regular visits to many of the smaller villages of Tianad, stealing and pillaging from merchants and private homes alike. 

For some time, people still hoped that the king would send reinforcements from his Dragon Guard to get the situation under control -- but reinforcements never came, and the few and in between remaining dragon guard soldiers stationed in Tianad soon disappeared. 

\medskip

But amidst the resignation and fear, there's still hope. Adventurers of all professions gather in the guilds and inns all over Tianad, wondering what can be done about the situation. Wondering why there is no word from the borders. Wondering what happened to the king's Dragon Guard. Wondering where the monster gangs are coming from.

And now, there's a rumour going around that in the remote city of Foxhome, a band of brave and intrepid adventurers has gathered to head off and find answers to all of these questions\dots and to save the once prosperous province of Tianad.

\end{document} 